Understanding Probabilistic Topic Models by Simulation

### 2017-12-10 simulations.Rmd
graphs with emojis

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(MCMCpack)
library(Compositional)
library(data.table)
library(utf8)
#install.packages("emojifont")
#library(emojifont)
library(htmlTable)
```

@@

```{r}
dd=data.frame(x=topic_labels, y=mixture_proportion)

ggplot(dd, aes(x, y)) + geom_col(fill="blue",alpha=.6) + 
  #theme(axis.text.x = emoji_text) + 
  labs(x="", y="", title="Mixture Proportions") 
```

```{r}
dd <- as.data.frame(topics)
names(dd) <- vocabulary
dd$topic_label <- topic_labels

melt(dd, id.vars="topic_label") %>%
  ggplot(aes(x=as.factor(topic_label), y=value, fill=variable)) +
  geom_col(position = "dodge") +
    #theme(axis.text.x = emoji_text,
    #      legend.text = emoji_text) +
    labs(x="", y="", title="Mixture Proportions", fill="")  
```

@@

# Generate documents
for (doc_index in 1:i) {
  topic = sample(topic_labels, 1, p=mixture_proportions)
  topic_num <- append(topic_num, topic)

>>>>

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(MCMCpack)
library(Compositional)
library(data.table)
#library(utf8)
#library(emojifont)
#library(htmlTable)
```

@@

```{r eval=FALSE, include=FALSE}
#list.emojifonts()
#load.emojifont('OpenSansEmoji.ttf')

emoji_text=element_text(family="OpenSansEmoji", size=20)

dd=data.frame(x=emoji(topic_labels), y=mixture_proportion)

ggsave(plot={
  ggplot(dd, aes(x, y)) + geom_col(fill="blue",alpha=.6) + 
  theme(axis.text.x = emoji_text) + 
  labs(x="", y="", title="Mixture Proportions") 
},
file = "images/simulations-1.png", dpi=600,
width = 7, height = 4
)
```

![Mixture Proportions](images/simulations-1.png)

```{r eval=FALSE, include=FALSE}
dd <- as.data.frame(topics)
names(dd) <- emoji(vocabulary)
dd$topic_label <- emoji(topic_labels)

ggsave(plot={
  melt(dd, id.vars="topic_label") %>%
  ggplot(aes(x=as.factor(topic_label), y=value, fill=variable)) +
  geom_col(position = "dodge") +
    theme(axis.text.x = emoji_text,
          legend.text = emoji_text) +
    labs(x="", y="", title="Mixture Proportions", fill="") 
},
file="images/simulations-2.png",
dpi = 600,
width=7,
height = 4
)
```
![Mixture Proportions 2](images/simulations-2.png)

@@

# Generate documents
for (doc_index in 1:i) {
  topic = sample(topic_labels, 1, p=mixture_proportion)
  topic_num <- append(topic_num, topic)
